Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-18 paper.tex
Rework challenges

Check Power to people and use it as bases for challenge discussion.

One important challenge for using Interactive Machine Learning is to translate the
state-action space between the human view and the algorithm view. This is a
reason why many researchers in IML focuse on limiting the human impact
to providing reward~\cite{knox2009interactively} or kinesthetic demonstrations
in the robot space~\cite{billard2008robot}. However as shown by Thomaz and Breazeal~\cite{thomaz2008teachable}, using more complex inputs from the supervisor, such
as guidance biasing the action selection can lead to a better performance in the
learning. However, to able to use these higher level and more complex inputs from
humans, these actions have to be translated in inputs usable for the learning
algorithm and/or the action selection mechanism.

The more complex the inputs from the humans are the more additional information
can be transmitted to the learning, allowing the agent to learn more complex
behaviours faster.

Similarly, as shown by Senft and al. in \cite{senft2017supervised}, providing
more control to the supervisor about the robot actions can lead to keep the
agent in relevant states of the environment and as such speeding the learning
and making it safer for the robot and people interacting with it. However this
method is dependent of letting the human know what action the robot is about to
execute, which relies on the robot to express its intention in a human
understandable way. (ADDREF - see Serge?)

Another challenge is state representation, the state accessed by the learning
algorithm and the one accessed by the supervisor can be represented is highly
different space, covering different features, and if the robot aims to profit
from the human initial knowledge, it needs to have access to similar features in
the environment to the ones the human is using, and the human needs to be able
to transmit these features to the learning algorithm.
(the representation of the state is often engineered by the programmers of the
algorithm, and space features not considered in the initial design could
actually be important in the final one. Idea of Deep Learning, but not enough
datapoints.)

Needs a parallel to human learning from humans

>>>>

A large body of the
Interactive Machine Learning research is focused on simple inputs from the
humans, such as providing labels \cite{cakmak2012designing}, rewards
\cite{knox2009interactively} or kinesthetic demonstrations
\cite{billard2008robot}. However, as stated in \cite{amershi2014power}: "people
want to demonstrate how learners should behave" and "users may desire richer
control over machine-learning systems than simply labeling data". Human teachers
want to be more active and involved in the teaching process, to make their
student learning faster. 
And, as shown in \cite{senft2017supervised}, providing teacher with this control
can keep the agent in relevant states of the environment, speeding the learning
and reducing the risk to have the robot execute undesired actions.

In human social learning, both interactants have access to a similar set of
inputs: the senses available to a human body, and the teacher has additional
knowledge about the environment that can be communicated in an open ended way to
the learner. On the other in human-robot teaching, the way to sense the world
can be highly different between the two partners, and as of today, there is no
open ended way of communicating new concepts or explication as natural langage
processing is not yet solve. This creates two main challenges to make robot
learning for human use complex inputs: 
\begin{itemize}
    \item Having a mapping between the action state space of the human and the
            robot ensuring that feature used for action selection for one
            interactant are available to the other.
    \item Communicating these features from one participant to the other: allow
        the robot to make sense of the human's instructions and the human to
        understand the robot's intentions.
\end{itemize}
